PyQBench: a Python library for benchmarking gate-based quantum computers

### 2023-04-13 txt/manuscript_short.tex
Update shortened manuscript

We introduce PyQBench, an innovative open-source framework for benchmarking
gate-based quantum computers. PyQBench can benchmark NISQ devices by verifying their capability of
discriminating between two von Neumann measurements. PyQBench offers a simplified, ready-to-use,
command line interface (CLI) for running benchmarks using a predefined parametrized Fourier
family of measurements. For more advanced scenarios, PyQBench offers a way of employing user-defined
measurements instead of predefined ones.

@@

% In
% cross--entropy benchmarkig a random quantum circuit is executed on a quantum computer multiple
% times. Then, the obtained measurement outcomes are used for computing cross--entropy fidelity
% $F_{XEB} \in [0, 1]$. A value of 0 means that results obtained from the device are no better then
% random guessing, whereas value of 1 correspond to a perfect, noiseless execution of the circuit.
% Packages implementing cross--entropy benchmarking include e.g. \cite{cross-entropy-bench}.

@@

In this section we describe how the benchmarking process in PyQBench works. To do so, we first
discuss necessary mathematical preliminaries. Then, we present the general form of the
discrimination scheme used in PyQBench and practical considerations on how to implement it taking
into account limitations of the current NISQ devices.

\subsection{Mathematical preliminaries}\label{sec:maths}

Let us first recall the definition of a von Neumann measurement, which is the only type of
measurement used in PyQBench. A von Neumann measurement $\PP$ is a collection of rank--one projectors
$\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$, called effects, that sum up to identity,
i.e. $ \, \, \sum_{i=0}^{d-1} \proj{u_i} = \1$. If $U$ is a unitary matrix of size $d$,
one can construct a von Neumann measurement $\PP_{U}$ by taking projectors onto its columns. In this
case we say that $\PP_{U}$ is described by the matrix $U$.

@@

In general, the discrimination scheme presented in Fig.~\ref{fig:theoretical_scheme}, requires an
auxiliary qubit. First, the joint system is prepared in some state $\ket{\psi_0}$. Then, one of the 
measurements,  either $\PP_U$ or $\PP_\1$, is performed on the first part of the system. Based on its
outcome $i$, we choose another POVM $\mathcal{P}_{V_i}$ and perform it on the second
qubit, obtaining the output in $j$. Finally, if $j=0$, we say that the performed measurement is
$\mathcal{P}_U$, otherwise we say that it was $\mathcal{P}_\Id$. Naturally, we need to repeat the
same procedure multiple times for both measurements to obtain a reliable estimate of the underlying
probability distribution. In PyQBench, we assume that the experiment is repeated the same number of
times for both $\PP_U$ and $\PP_\Id$.

@@

@@

The second idea uses the direct sum $V_0^\dagger \oplus V_1^\dagger$ implementation.     Here, instead of performing a conditional
measurement $\PP_{V_k}$, where $k\in \{0,1\}$,  we run circuits presented in
Fig.~\ref{fig:controlled}.

	\begin{figure}[h!]
		\centering
		\includegraphics[width=0.8\textwidth]{pics/controlled_unitary}

@@

\subsubsection{Importance of choosing the optimal discrimination scheme}
In principle, the schemes described in the previous section could be used with any choice of
$\ket{\psi_0}$ and final measurements $\PP_{V_i}$. However, we argue that it is best to choose those
components in such a way that they maximize the probability of correct discrimination. To see that,
suppose that some choice of $\ket{\psi_0}, \PP_{V_0}, \PP_{V_1}$ yields the theoretical upper bound
of discriminating between two measurements of one, i.e. on a perfect quantum computer you will always
make a correct guess. Then, on real hardware, we might obtain any empirical value in range $\left[\frac{1}{2},
1\right]$. On the other hand, if we choose the components of our scheme such that the successful
discrimination probability is only $\frac{3}{5}$, the possible range of empirically obtainable probabilities
is only $\left[\frac{1}{2}, \frac{3}{5}\right]$. Hence, in the second case, the discrepancy between theoretical and empirical
results will be less pronounced.

\subsubsection{Constructing optimal discrimination scheme}
To construct the optimal discrimination scheme, one starts by calculating the probability of correct discrimination. Using the celebrated result by Helstrom~\cite{helstrom1976quantum}, one finds that the  optimal probability of correct discrimination between two quantum measurements, $\PP$  and $\mathcal{Q}$, is
\begin{equation}
p_{\text{succ}}(\PP, \mathcal{Q}) =  \frac12 + \frac14 \| \PP - \mathcal{Q} \|_\diamond,
\end{equation}
where
\begin{equation}
\|\PP - \QQ\|_\diamond = \max_{\| \ket{\psi}\|_1=1} \| \left( (\PP - \QQ) \otimes \1\right) (\proj{\psi}) \|_1.
\end{equation}
The quantum state $\ket{\psi_0}$ maximizing the diamond norm above is called the
\emph{discriminator}, and can be computed e.g. using semidefinite programming (SDP)
\cite{watrous,watrous2021simplier}. Furthermore,  using the proof of the Holevo-Helstrom theorem, it is
possible to construct corresponding unitaries $V_0$, $V_1$ to create the optimal
discrimination strategy. For brevity, we do not describe this procedure here. Instead, we refer the
interested reader to \cite{watrous}.

@@

The PyQBench library also contains a readily available implementation of all necessary components
needed to run discrimination experiments for parametrized Fourier family of measurements, defined
previously in Section \ref{sec:fourier}. However, if one only wishes to use this particular family
of measurements in their benchmarks, then using PyQBench as a command line tool might be more straightforward. PyQBench's command line interface allows running the benchmarking process without
writing Python code. The configuration of CLI is done by YAML \cite{yaml} files describing the benchmark
to be performed and the description of the backend on which the benchmark should be run. Notably,
the YAML configuration files are reusable. The same benchmark can be used with different backends
and vice versa.

The following section describes important architectural decisions taken when creating PyQBench, and
how they affect the end-user experience.

@@

The Command Line Interface (CLI) of PyQBench has nested structure. The general form of the CLI
invocation is shown in listing \ref{lst:cli}.
\begin{lstlisting}[caption=Invocation of \texttt{qbench} script, label=lst:cli]
qbench <benchmark-type> <command> <parameters>
\end{lstlisting}
Currently, PyQBench's CLI supports only one type of benchmark (discrimination of parametrized
Fourier family of measurements), but we decided on structuring the CLI in a hierarchical
fashion to allow for future extensions. Thus, the only accepted value of \texttt{<benchmark-type>}
is \texttt{disc-fourier}.
%
The \texttt{qbench disc-fourier} command has four subcommands:

@@

\subsection{Using \texttt{qbench} CLI}
Using PyQBench as a library allows one to conduct a two--qubits benchmark with arbitrary von Neumann
measurement. However, as discussed in the previous guide, it requires writing some amount of code.
For a Fourier parametrized family of measurements, PyQBench offers a simplified way of conducting
benchmarks using a Command Line Interface (CLI). The workflow with PyQBench's CLI can be summarized
as the following list of steps::

\begin{enumerate}

\item Preparing configuration files describing the backend and the experiment scenario.
\item Submitting/running experiments. Depending on the experiment scenario, execution can be synchronous, or asynchronous.
\item (optional) Checking the status of the submitted jobs if the execution is asynchronous.
\item Resolving asynchronous jobs into the actual measurement outcomes.
\item Converting obtained measurement outcomes into tabulated form.
\end{enumerate}
\subsubsection{Preparing configuration files}
The configuration of PyQBench CLI is driven by YAML files. The first configuration file
describes the experiment scenario to be executed. The second file describes the backend.
Typically, this backend will correspond to the physical device to be benchmarked, but for testing
purposes one might as well use any other Qiskit--compatible backend including simulators.
Let us first describe the experiment configuration file, which might look as follow.
\begin{lstlisting}[language=Python, caption=Defining the experiment, label=lst:experiment]
type: discrimination-fourier
qubits:
	- target: 0
	  ancilla: 1
	- target: 1
      ancilla: 2
angles:
	start: 0
	stop: 2 * pi
	num_steps: 3
gateset: ibmq
method: direct_sum
num_shots: 100
\end{lstlisting}

@@

\subsubsection{Running the experiment and collecting measurements data}
After preparing YAML files defining experiment and backend,
running the benchmark can be launched by using the following command line invocation:
\begin{lstlisting}[language=Python]
qbench disc-fourier benchmark experiment_file.yml backend_file.yml
\end{lstlisting}
The output file will be printed to stdout. Optionally, the \texttt{- -output OUTPUT} parameter might be provided to write the output to the \texttt{OUTPUT} file instead.
\begin{lstlisting}[language=Python]
qbench disc-fourier benchmark experiment_file.yml backend_file.yml --output async_results.yml
\end{lstlisting}
The result of running the above command can be twofold:
\begin{itemize}
	\item If backend is asynchronous, the output will contain intermediate data containing, amongst others, \texttt{job\_ids} correlated with the circuit they correspond to.
	\item If the backend is synchronous, the output will contain measurement outcomes (bitstrings) for each of the circuits run.
\end{itemize}

For synchronous experiment, the part of output looks similar to the one below. The whole YAML file can be seen in \ref{app:example}.
%Consider the particular experiment data
\begin{lstlisting}[language=Python]
data:
- target: 0
  ancilla: 1
  phi: 0.0
  results_per_circuit:
  - name: id
  histogram: {'00': 28, '01': 26, '10': 21, '11': 25}
  mitigation_info:
	target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
	ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
  mitigated_histogram: {'00': 0.2637212373658018, '01': 0.25865061319892463, '10': 0.2067279352110304, '11': 0.2709002142242433}
\end{lstlisting}

@@

% \begin{thebibliography}{00}
% \bibitem{preskill} Preskill, J. (2018). Quantum Computing in the NISQ era and beyond. Quantum 2, 79.
% \bibitem{rigetti} The web resource at \url{https://www.rigetti.com/}. Accessed on 2023-02-18.
% \bibitem{ibmq} The web resource at \url{https://www.ibm.com/quantum}. Accessed on 2023-02-18.
% \bibitem{oxforf} The web resource at \url{http://oxfordquantum.org/}. Accessed on 2023-02-18.
% \bibitem{ionq} The web resource at \url{https://ionq.com/}. Accessed on 2023-02-18.
% \bibitem{xanadu} The web resource at \url{https://www.xanadu.ai/}. Accessed on 2023-02-18.
% \bibitem{dwave} The web resource at \url{https://www.dwavesys.com/}. Accessed on 2023-02-18.
% \bibitem{quera} The web resource at \url{https://www.quera.com/}. Accessed on 2023-02-18.
% \bibitem{sdk} The web resource at \url{https://docs.rigetti.com/qcs/}. Accessed on 2023-02-18.
% \bibitem{pyquil} The web resource at \url{https://pyquil-docs.rigetti.com/en/stable/}. Accessed on 2023-02-18.
% \bibitem{qiskit} The web resource at \url{https://qiskit.org/}. Accessed on 2023-02-18.
% \bibitem{ibmqplatform} The web resource at \url{https://quantum-computing.ibm.com/}. Accessed on 2023-02-18.
% \bibitem{amazon} The web resource at \url{https://aws.amazon.com/braket/}. Accessed on 2023-02-18.
% \bibitem{zapata} The web resource at \url{https://www.zapatacomputing.com/orquestra-platform/}. Accessed on 2023-02-18.
% \bibitem{preskillnew} Preskill, J. (2021). Quantum computing 40 years later. arXiv preprint arXiv:2106.10522.
% \bibitem{liu2022sampling} 	Liu, Y., Otten, M., Bassirianjahromi, R., Jiang, L.,  Fefferman, B. (2021). Benchmarking near-term quantum computers via random circuit sampling. arXiv preprint arXiv:2105.05232.
% \bibitem{knill2008randomized}
% Knill, E., Leibfried, D., Reichle, R., Britton, J., Blakestad, R. B., Jost, J. D., Langer, C., Ozeri, R., Seidelin, S.,  Wineland, D. J. (2008). Randomized benchmarking of quantum gates. Physical Review A, 77(1), 012307.
% \bibitem{wallman2014randomized} Wallman, J. J.,  Flammia, S. T. (2014). Randomized benchmarking with confidence. New Journal of Physics, 16(10), 103032.
% \bibitem{helsen2022general} Helsen, J., Roth, I., Onorati, E., Werner, A. H.,  Eisert, J. (2022). General framework for randomized benchmarking. PRX Quantum, 3(2), 020357.
% \bibitem{cornelissen2021scalable} Cornelissen, A., Bausch, J.,  Gilyén, A. (2021). Scalable benchmarks for gate-based quantum computers. arXiv preprint arXiv:2104.10698.
% \bibitem{cross2019validating}
% Cross, A. W., Bishop, L. S., Sheldon, S., Nation, P. D., Gambetta, J. M. (2019). Validating quantum computers using randomized model circuits. Physical Review A, 100(3), 032328.
% \bibitem{moll2018quantum}
% Moll, N., Barkoutsos, P., Bishop, L. S., Chow, J. M., Cross, A., Egger, D. J., Filipp, S., Fuhrer, A., Gambetta, J. M., Ganzhorn, M., Kandala, A., Mezzacapo, A., M{\"u}ller, P., Riess, W., Salis, G., Smolin, J., Tavernelli, I.,  Temme, K. (2018). Quantum optimization using variational algorithms on near-term quantum devices. Quantum Science and Technology, 3(3), 030503.
% \bibitem{pelofske2022volume} Pelofske, E., Bärtschi, A.,  Eidenbenz, S. (2022). Quantum volume in practice: What users can expect from NISQ devices. IEEE Transactions on Quantum Engineering, 3, 1-19.
% 	\bibitem{mqt2022} Quetschlich, N., Burgholzer, L., Wille, R. (2022). MQT Bench: Benchmarking software and design automation tools for quantum computing. arXiv preprint arXiv:2204.13719.
% \bibitem{mqt-bench} The web resource at  \url{https://github.com/cda-tum/MQTBench}. Accessed on 2023-02-18.
% 	\bibitem{supermarq} Tomesh, T., Gokhale, P., Omole, V., Ravi, G. S., Smith, K. N., Viszlai, J., Wu, X.,  Hardavellas, N., Martonosi, M.R.,  Chong, F. T. (2022). Supermarq: A scalable quantum benchmark suite. In 2022 IEEE International Symposium on High-Performance Computer Architecture (HPCA) (pp. 587-603). IEEE.
% \bibitem{supermarkq-github} The web resource at \url{https://github.com/SupertechLabs/SupermarQ}. Accessed on 2023-02-18.
% \bibitem{qiskit-randomized} The web resource at
% \url{https://github.com/qiskit-community/qiskit-benchmarks}. Accessed on 2023-02-18.
% \bibitem{forest-benchmarking} The web resource at \url{https://github.com/rigetti/forest-benchmarking}. Accessed on 2023-02-18.
% \bibitem{volume-in-practice} The web resource at \url{https://github.com/lanl/Quantum-Volume-in-Practice}. Accessed on 2023-02-18.
% \bibitem{cross-entropy-bench} The web resource at
% \url{https://quantumai.google/cirq/noise/qcvv/xeb_theory}.  Accessed on 2023-02-18.
% \bibitem{puchala2018strategies} Puchała, Z.,  Pawela, Ł.,  Krawiec, A.,  Kukulski, R. (2018). Strategies for
% optimal single-shot discrimination of quantum measurements. Physical Review A
% 98.4, 042103.
% \bibitem{watrous} Watrous, J. (2018). The theory of quantum information. Cambridge University Press.
% \bibitem{helstrom1976quantum} Helstrom, C. W. (1969). Quantum detection and estimation theory. Journal of Statistical Physics, 1(2), 231-252.
% \bibitem{yaml} The web resource at \url{https://yaml.org/spec/1.2.2/}. Accessed on 2023-02-18.
% \bibitem{pyqbenchgithub} The web resource at \url{https://github.com/iitis/PyQBench}. Accessed on 2023-02-18.
% \bibitem{pyqbenchgithub} The web resource at \url{https://github.com/iitis/PyQBench}. Accessed on 2023-02-18.
% \bibitem{pyqbenchdocs} The web resource at \url{https://pyqbench.readthedocs.io/en/latest/}. Accessed on 2023-02-18.
% \bibitem{qiskit-braket-provider} The web resource at \url{https://aws.amazon.com/blogs/quantum-computing/introducing-the-qiskit-provider-for-amazon-braket/}. Accessed on 2023-02-18.
% \bibitem{qiskit-braket-provider-github} The web resource at \url{https://github.com/qiskit-community/qiskit-braket-provider}. Accessed on 2023-02-18.
% \bibitem{aer} The web resource at \url{https://github.com/Qiskit/qiskit-aer}. Accessed on 2023-02-18.
% \bibitem{mthree} The web resource at \url{https://qiskit.org/documentation/partners/mthree/stubs/mthree.M3Mitigation.html}. Accessed on 2023-02-10.
% \bibitem{mthreepublication} Nation, P. D., Kang, H., Sundaresan, N.,  Gambetta, J. M. (2021). Scalable mitigation of measurement errors on quantum computers. PRX Quantum, 2(4), 040326.
% \bibitem{numericalrangle} Murnaghan, F. D. (1932). On the field of values of a square matrix. Proceedings of the National Academy of Sciences, 18(3), 246-248.
% \bibitem{nr} The web resource at \url{https://numericalshadow.org/}. Accessed on 2022-10-02.
% \bibitem{watrous2021simplier} Watrous, J. (2013). Simpler semidefinite programs for completely bounded norms. Chicago Journal of Theoretical Computer Science, 8.
% \bibitem{lewandowska2021certification} Lewandowska, P., Krawiec, A., Kukulski, R., Pawela, Ł.,  Puchała, Z. (2021). On the optimal certification of von Neumann measurements. Scientific Reports, 11(1), 3623.
% \bibitem{hausdorff} Hausdorff, F. (1919). Der wertvorrat einer bilinearform. Mathematische Zeitschrift, 3(1), 314-316.
% \bibitem{toeplitz} Toeplitz, O. (1918). Das algebraische Analogon zu einem Satze von Fejér. Mathematische Zeitschrift, 2(1-2), 187-197.
% \bibitem{michielsen2017benchmarking} Michielsen, K., Nocon, M., Willsch, D., Jin, F., Lippert, T.,  De Raedt, H. (2017). Benchmarking gate-based quantum computers. Computer Physics Communications, 220, 44-55.
% \bibitem{zhukov2019quantum} Zhukov, A. A., Kiktenko, E. O., Elistratov, A. A., Pogosov, W. V.,  Lozovik, Y. E. (2019). Quantum communication protocols as a benchmark for programmable quantum computers. Quantum Information Processing, 18(1), 31.
% \bibitem{hamilton2018generative} Hamilton, Kathleen E., Eugene F. Dumitrescu,
% and Raphael C. Pooser. (2019). Generative model benchmarks for superconducting
% qubits. Physical Review A 99(6), 062323.
% \bibitem{benedetti2018generative} Benedetti, M., Garcia-Pintos, D., Perdomo, O., Leyton-Ortega, V., Nam, Y., Perdomo-Ortiz, A. (2019). A generative modeling approach for benchmarking and training shallow quantum circuits. npj Quantum Information, 5(1), 45.

% \end{thebibliography}

>>>>

We introduce PyQBench, an innovative open-source framework for benchmarking gate-based quantum
computers. PyQBench can benchmark NISQ devices by verifying their capability of discriminating
between two von Neumann measurements. PyQBench offers a simplified, ready-to-use, command line
interface (CLI) for running benchmarks using a predefined family of measurements. For more advanced
scenarios, PyQBench offers a way of employing user-defined measurements instead of predefined ones.

@@

@@

In this section, we describe how the benchmarking process in PyQBench works. We start by
discussing necessary mathematical preliminaries. Then, we present the general form of the
discrimination scheme used in PyQBench and practical considerations on how to implement it taking
into account the limitations of the current NISQ devices.

\subsection{Von Neumann Measurements}\label{sec:maths}

A von Neumann measurement $\PP$ is a collection of rank--one projectors
$\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$, called effects, that sum up to the identity operator, i.e.
$ \, \, \sum_{i=0}^{d-1} \proj{u_i} = \1$. If $U$ is a unitary matrix of size $d$, one can construct
a von Neumann measurement $\PP_{U}$ by taking projectors onto its columns. In this case we say that
$\PP_{U}$ is described by the matrix $U$.

@@

The discrimination scheme presented in Fig.~\ref{fig:theoretical_scheme} requires an
auxiliary qubit. First, the joint system is prepared in some state $\ket{\psi_0}$. Then, one of the
measurements, either $\PP_U$ or $\PP_\1$, is performed on the first part of the system. Based on its
outcome $i$, we choose another measurement $\mathcal{P}_{V_i}$ and perform it on the second qubit,
obtaining the outcome $j$. Finally, if $j=0$, we say that the performed measurement is
$\mathcal{P}_U$, otherwise we say that it was $\mathcal{P}_\Id$. Naturally, we need to repeat the
same procedure multiple times for both measurements to obtain a reliable estimate of the underlying
probability distribution. In PyQBench, we assume that the experiment is repeated the same number of
times for both $\PP_U$ and $\PP_\Id$.

@@

In principle, our discrimination scheme could be used with any choice of
$\ket{\psi_0}$ and final measurements $\PP_{V_i}$. However, we argue that it is best to choose those
components so that they maximize the probability of correct discrimination. To see that,
suppose that some choice of $\ket{\psi_0}, \PP_{V_0}, \PP_{V_1}$ allows for correctly discriminating
between two measurements with probability equal to one, i.e. on a perfect quantum computer you will always
make a correct guess. Then, on real hardware, we might obtain any empirical value in range $\left[\frac{1}{2},
1\right]$. On the other hand, if we choose the components of our scheme such that the successful
discrimination probability is $\frac{3}{5}$, the possible range of empirically obtainable probabilities
is only $\left[\frac{1}{2}, \frac{3}{5}\right]$. Hence, in the second case, the discrepancy between theoretical and empirical
results will be less pronounced.

@@

The second idea uses the direct sum $V_0^\dagger \oplus V_1^\dagger$ implementation. Here, instead
of performing a conditional measurement $\PP_{V_k}$, where $k\in \{0,1\}$,  we run circuits
presented in Fig.~\ref{fig:controlled}.
	\begin{figure}[h!]
		\centering
		\includegraphics[width=0.8\textwidth]{pics/controlled_unitary}

@@

% \subsubsection{Constructing optimal discrimination scheme}
% To construct the optimal discrimination scheme, one starts by calculating the probability of correct discrimination. Using the celebrated result by Helstrom~\cite{helstrom1976quantum}, one finds that the  optimal probability of correct discrimination between two quantum measurements, $\PP$  and $\mathcal{Q}$, is
% \begin{equation}
% p_{\text{succ}}(\PP, \mathcal{Q}) =  \frac12 + \frac14 \| \PP - \mathcal{Q} \|_\diamond,
% \end{equation}
% where
% \begin{equation}
% \|\PP - \QQ\|_\diamond = \max_{\| \ket{\psi}\|_1=1} \| \left( (\PP - \QQ) \otimes \1\right) (\proj{\psi}) \|_1.
% \end{equation}
% The quantum state $\ket{\psi_0}$ maximizing the diamond norm above is called the
% \emph{discriminator}, and can be computed e.g. using semidefinite programming (SDP)
% \cite{watrous,watrous2021simplier}. Furthermore,  using the proof of the Holevo-Helstrom theorem, it is
% possible to construct corresponding unitaries $V_0$, $V_1$ to create the optimal
% discrimination strategy. For brevity, we do not describe this procedure here. Instead, we refer the
% interested reader to \cite{watrous}.

@@

The PyQBench library also contains a readily available implementation of all necessary components
needed to run discrimination experiments for parametrized Fourier family of measurements (see
\cite{appendix}). However, if one only wishes to use this particular family of measurements in their
benchmarks, then using PyQBench as a command line tool might be more straightforward. PyQBench's
command line interface allows running the benchmarking process without writing Python code. The
configuration of CLI is done by YAML \cite{yaml} files describing the benchmark to be performed and
the description of the backend on which the benchmark should be run. The same benchmark can be used
with different backends and vice versa.

@@

The Command Line Interface (CLI) of PyQBench has nested structure. The general form of the CLI
invocation is shown in listing \ref{lst:cli}.
\begin{lstlisting}[caption=Invocation of \texttt{qbench} script, label=lst:cli]
qbench <benchmark-type> <command> <parameters>
\end{lstlisting}
Currently, PyQBench's CLI supports only one type of benchmark (discrimination of parametrized
Fourier family of measurements), but we decided on hierarchically structuring the CL to allow for
future extensions. Thus, the only accepted value of \texttt{<benchmark-type>} is
\texttt{disc-fourier}.
%
The \texttt{qbench disc-fourier} command has four subcommands:

@@

\subsection{Using \texttt{qbench} CLI}
Using PyQBench as a library allows one to conduct a two--qubits benchmark with arbitrary von Neumann
measurement. However, as discussed in the previous guide, it requires writing some amount of code.
For a Fourier parametrized family of measurements, PyQBench offers a simplified way of conducting
benchmarks using a Command Line Interface (CLI). The workflow with PyQBench's CLI can be summarized
as the following list of steps:

\begin{enumerate}
  \item Preparing configuration files describing the backend and the experiment scenario.
  \item Submitting/running experiments. Depending on the experiment scenario, execution can be
		synchronous, or asynchronous.
  \item (optional) Checking the status of the submitted jobs if the execution is asynchronous.
  \item Resolving asynchronous jobs into the actual measurement outcomes.
  \item Converting obtained measurement outcomes into tabulated form.
\end{enumerate}
\subsubsection{Preparing configuration files}
The configuration of PyQBench CLI is driven by YAML files. The first configuration file describes
the experiment scenario to be executed. The second file describes the backend. Typically, this
backend will correspond to the physical device to be benchmarked, but for testing purposes, one
might as well use any other Qiskit--compatible backend including simulators. Let us first describe
the experiment configuration file, which might look as follow.
\begin{lstlisting}[language=Python, caption=Defining the experiment, label=lst:experiment]
type: discrimination-fourier
qubits:
	- target: 0
	  ancilla: 1
	- target: 1
      ancilla: 2
angles:
	start: 0
	stop: 2 * pi
	num_steps: 3
gateset: ibmq
method: direct_sum
num_shots: 100
\end{lstlisting}

@@

\subsubsection{Running the experiment and collecting measurements data}
After preparing YAML files defining experiment and backend,
running the benchmark can be launched by using the following command line invocation:
\begin{lstlisting}[language=Python]
qbench disc-fourier benchmark experiment_file.yml backend_file.yml
\end{lstlisting}
The output file will be printed to stdout. Optionally, the \texttt{- -output OUTPUT} parameter might
be provided to write the output to the \texttt{OUTPUT} file instead.
\begin{lstlisting}[language=Python]
qbench disc-fourier benchmark experiment_file.yml backend_file.yml --output async_results.yml
\end{lstlisting}
The result of running the above command can be twofold:
\begin{itemize}
	\item If the backend is asynchronous, the output will contain intermediate data containing, amongst
		others, \texttt{job\_ids} correlated with the circuit they correspond to.
	\item If the backend is synchronous, the output will contain measurement outcomes (bitstrings)
		for each of the circuits run.
\end{itemize}

For the synchronous experiment, the part of output looks similar to the one below. The whole YAML
file can be seen in \ref{app:example}.
%Consider the particular experiment data
\begin{lstlisting}[language=Python]
data:
- target: 0
  ancilla: 1
  phi: 0.0
  results_per_circuit:
  - name: id
  histogram: {'00': 28, '01': 26, '10': 21, '11': 25}
  mitigation_info:
	target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
	ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
  mitigated_histogram: {'00': 0.2637212373658018, '01': 0.25865061319892463, '10': 0.2067279352110304, '11': 0.2709002142242433}
\end{lstlisting}

@@
